---
title: "Reticulate Basics"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA)
library(reticulate)
library(dplyr)
```

# Setting up our environment

Environments are a way to minimize package conflicts between your projects. I can start with a clean installation of python, and any packages I require. 

```{r}
# what environments are present?
envs = conda_list()
# Create an environment, latest python, with a compatible pandas package.
if (! 'reticulate-satrday' %in% envs$name) {
    conda_create('reticulate-satrday', packages = 'pandas')
}
# use the env we just created:
use_condaenv('reticulate-satrday', required = TRUE)
```

Now we're ready to use python from R!

# Using python

## Using python directly

We can start a REPL (read-evaluate-print-loop) to do python things directly in a 
python console, just like in the R console.

```{r, eval = FALSE}
repl_python()
# import os
# os.getcwd()
```

## Using python in a code chunk

I can run python directly, in this code chunk!

```{python}
# This is native python code!
import os
import numpy as np # for later
os.getcwd()
```

I can also use python modules directly from R (take note of the language in the code chunk fence):

```{r}
# ^^^^ this is R!
os = import('os') # Import the python module __into__ R 
os$getcwd()
```

## Executing arbitrary python code

I run some code using `py_run_string`, which is executed in the environment we
started up just now. Even though the REPL was closed, the session persists. We
can flip back and forth as we like.

There is an object called `py` that lets us access objects from the python
session -- converted immediately to native R objects! So the object `vec` that 
we made in python is now accessible to us in R.

```{r}
py_run_string('vec = np.arange(1,10).tolist()')
# Access python objects from R!
message("This is python converted to an R object")
py$vec
```

Compare to the same object, generated in R:

```{r}
rvec = seq(1,9)
message("R vector same as python vector")
all.equal(rvec, py$vec)
```

## Accessing R stuff from python

Now we'll load the `CO2` dataset, which is a `data.frame` built into R.

```{r}
data(CO2)
```

I can use the `r` module to get items from R, the same way I used the `py` object in R to get other stuff from the active python session.

```{python}
rvec_in_python = r.__getitem__('rvec')
type(rvec_in_python)
rvec_in_python
```

```{python}
df_in_python = r.__getitem__('CO2')
type(df_in_python)
df_in_python
```

